COG-ED Manuscript

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
excluded subject M28B11

@@

@@

The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).

@@

>>>>

  # remove one subject who did not understand the instructions of the n-back task and reacted only to every n-th stimulus

  data_nback <- data_nback[data_nback$subject != "M28B11", ]
  data_ED <- data_ED[data_ED$subject != "M28B11", ]

@@

  # remove the subject who misunderstood the instruction

  data_quest <- data_quest[data_quest$set != "M28B11", ]

@@

The sample of the pilot study consisted of $N=$ `r length(setindex)` participants (`r round((table(data_quest$gender)[2]/length(setindex))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=$ `r length(setindex)-1` data sets.

@@

  levelindex <- c(1,which(pipelines_data[["AARO"]]$level != dplyr::lag(pipelines_data[["AARO"]]$level)),nrow(pipelines_data[["AARO"]]))
